Redundant calibration as a complex optimization problem

### 2016-12-08 paper.tex
added some text to simulation section

\begin{table*}
\centering
\caption{The following fixed simulation parameters were used to generate the results of this paper.}
\begin{tabular}{|c c c c c c c|} 
\hline
Declination & Latitude & Minimum baseline & Geometry& Sources & Flux & Spatial \\
\hline 
\hline
 $-74^{\circ}39'37.481''$ & $-30^{\circ}43'17.34''$ & 20 & Hexagonal &100 & Pareto (shape param. of 2) & $U[-3,3]$ (deg.) 
\end{tabular}
\end{table*}

\begin{table}
\centering
\caption{We generated results using two major simulation setups. We either used one frequency channel and multiple time-slots, or one time-slot and many frequency 
channels. The most important parameters used in realizing these two major setups are presented here.}
\begin{tabular}{|c c c|} 
\hline
 & Setup 1 & Setup 2\\
\hline
\hline
 Num. channels & 1024 & 1\\
$\nu$-range & 100-200 MHz & 1.4 GHz\\
Num. timeslots & 1 & 50\\
%Hour angle &-1^h & [-1^h,1^h]\\
Gain error model & 2 & 1\\
\hline
\end{tabular}
\end{table}

\begin{table*}
\centering
\caption{The gain error models used in this paper. We have used the symbol $x$ here as a proxy as it can either refer to $t$ or $\nu$. We either
performed our simulations over multiple time-slots and one frequency channel or one timeslot and multiple frequencey channels. We use $U$ to represent 
a uniform distribution. Moreover, $c$ in the left most column denotes the speed of light.}
\begin{tabular}{|c c c c|} 
\hline
Number tag & 1 & 2 & 3\\
Model & Sinusoidal: amplitude and phase & Sinusoidal: real and imaginary parts & Linear phase slope \\ [0.5ex] 
\hline\hline
Function & $(A+1)e^{jP}$ & $A\cos(2\pi fx+B)+1.5A+jC\sin(2\pi fx+D)$ & $e^{jP}$ \\ 
\hline
Parameters & $A=a\cos(2\pi fx +b)$  & $f=5$ & $P=\tau x$ \\
 & $P =c \cos(2\pi fx +d)$ & $A,C\sim U[0.5,10]$ & $\tau = \frac{l}{c}$ \\
 & $f=5$ & $B,D\sim U[0,2\pi]$ &  $l\sim U[5,50]$ (m)\\
 & $a\sim U[0.8,0.9]$ &  & \\ 
 & $c\sim U[0.5,5]$ &  &  \\ 
 & $b,d\sim U[0,2\pi]$ &  &  \\ 
\hline
\end{tabular}
\end{table*}

>>>>

The results reported in this paper were generated using two major experimental setups, namely a single time-slot and multiple frequency channels setup or 
a single frquency channel and multiple time-slots setup. The simulation parameters which where kept fixed in both these setups can be found in 
Table~\ref{tab:fixed_parm}. The sky-model we used to simulate the visibilities were the same for both setups. We generated 100 sources, each source had random 
flux and position. The flux of the sources followed a Pareto distribution (with a shape parameter of 2), while their positions were uniformly 
distributed in a 3 by 3 degree square grid around the field center. We used a hexagonal redundant layout for our antenna positions. We produced 
results for different

\begin{table*}
\centering
\caption{The following fixed simulation parameters were used to generate the results of this paper.}
\begin{tabular}{|c c c c c c c|} 
\hline
Declination & Latitude & Minimum baseline & Geometry& Sources & Flux & Spatial \\
\hline 
\hline
 $-74^{\circ}39'37.481''$ & $-30^{\circ}43'17.34''$ & 20 & Hexagonal &100 & Pareto (shape param. of 2) & $U[-3,3]$ (deg.) 
\end{tabular}
\label{tab:fixed_parm}
\end{table*}

\begin{table}
\centering
\caption{We generated results using two major simulation setups. We either used one frequency channel and multiple time-slots, or one time-slot and multiple frequency 
channels. The most important parameters used in realizing these two major setups are presented here.}
\begin{tabular}{|c c c|} 
\hline
 & Setup 1 & Setup 2\\
\hline
\hline
 Num. channels & 1024 & 1\\
$\nu$-range & 100-200 MHz & 1.4 GHz\\
Num. timeslots & 1 & 50\\
%Hour angle &-1^h & [-1^h,1^h]\\
Gain error model (Table~\ref{tab:gain_parm}) & 2 & 1\\
\hline
\end{tabular}
\label{tab:ch_parm}
\end{table}

\begin{table*}
\centering
\caption{The gain error models used in this paper. We have used the symbol $x$ here as a proxy as it can either refer to time-slots or channels. We either
performed our simulations over multiple time-slots and one frequency channel or one timeslot and multiple frequencey channels. We use $U$ to represent 
a uniform distribution. Moreover, $c$ in the left most column denotes the speed of light.}
\begin{tabular}{|c c c c|} 
\hline
Number tag & 1 & 2 & 3\\
Model & Sinusoidal: amplitude and phase & Sinusoidal: real and imaginary parts & Linear phase slope \\ [0.5ex] 
\hline\hline
Function & $(A+1)e^{jP}$ & $A\cos(2\pi fx+B)+1.5A+jC\sin(2\pi fx+D)$ & $e^{jP}$ \\ 
\hline
Parameters & $A=a\cos(2\pi fx +b)$  & $f=5$ & $P=\tau x$ \\
 & $P =c \cos(2\pi fx +d)$ & $A,C\sim U[0.5,10]$ & $\tau = \frac{l}{c}$ \\
 & $f=5$ & $B,D\sim U[0,2\pi]$ &  $l\sim U[5,50]$ (m)\\
 & $a\sim U[0.8,0.9]$ &  & \\ 
 & $c\sim U[0.5,5]$ &  &  \\ 
 & $b,d\sim U[0,2\pi]$ &  &  \\ 
\hline
\end{tabular}
\label{tab:gain_parm}
\end{table*}
